---
title: "R Notebook"
output: github_document
---

```{r}
suppressPackageStartupMessages(library(palmerpenguins))
suppressPackageStartupMessages(library(lubridate))
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(testthat))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(gapminder))
suppressPackageStartupMessages(library(digest))
suppressPackageStartupMessages(library(datateachr))
```

exercise1&2

#' Basic data cleaning
#' @details this function deletes omitted observations and keeps observations above a threshold (for example: you can use 0 as the threshold and keep positive observations). 
#'
#' @keywords dataclean
#'
#' @param data the dataset to be cleaned
#' @param x the numeric vector to be cleaned
#' @param n the threshold used to clean data
#'
#' @return returns a cleaned dataset


```{r}
cleanr<-function(data,x,n){
  stopifnot(is.data.frame(data))
  if(!is.numeric(x)) {
    stop('this function only works for numeric input!\n',
         'You have provided an object of class: ', class(x)[1])
  }
  y<-data%>%
    filter(x>n)%>%
    drop_na()
  return(y)
}
```

exercise3
In this example, I use building permits dataset and keep the positive project value.
```{r}
cleanr(building_permits,building_permits$project_value,0)
```

I can also keep the project value higher than certain threshold. For example, I keep high-value project whose value is larger than 100,000.
```{r}
cleanr(building_permits,building_permits$project_value,100000)
```

I use a character type_of_work and get an error.
```{r, error=TRUE}
cleanr(building_permits,building_permits$type_of_work,0)
```


exercise4

building_permits$project_value has NA's, building_permits$type_or_work is a character vector, and cancer_sample$radius_mean has non NA's

```{r}
data1<-building_permits%>%
    filter(project_value>0)%>%
    drop_na()
data2<-building_permits%>%
    filter(type_of_work>0)%>%
    drop_na() 
data3<-cancer_sample%>%
    filter(radius_mean>10)%>%
    drop_na() 
```

```{r}
test_that("Testing function1", {
  expect_equal(cleanr(building_permits,building_permits$project_value,0),data1)})
```
```{r}
test_that("Testing function2", {
   expect_error(cleanr(building_permits,building_permits$type_of_work,0),"this function only works for numeric input!
You have provided an object of class: character")})
```
```{r}
test_that("Testing function3", {
   expect_equal(cleanr(cancer_sample,cancer_sample$radius_mean,10), data3)})
```
 
